A thesis draft

### 2018-11-27 res/sections/10-ProjectAnalysis.tex
Move Harbor section from 10 to 15. Add Harbor schema

\subsubsection{Harbor}
\label{chap:prjan:sec:tech:sub:MANO:sub:harbor}
Started as a VNFM (Virtual Network Function Virtualization Manager) to offer a
bridge for Openbaton to interact with Kubernetes, during the project it has been
expanded to become a complete replacement of the original product, adding the
possibility to manage Network Services and to update the routing tables
contained in the Roulette Controller (the tool description can be found below
in~\ref{chap:prjan:sec:tech:sub:SFC:sub:roulette}). Harbor doesn't have a web
interface, but it has a RESTful API that allows users to interact with it using
CRUD operations. It offers functionalities similar to Openbaton: possibility to
save and retrieve VNF and NS definitions (basically, Kubernetes YAML
deployments). When an NS is saved, a consistency check is performed to assure
that all the VNFs have already been defined in Harbor. On an NS deployment, with
a mechanism similar to the Openbaton one, all the associated VNFs are set up
too, making the whole operation of launching a NS atomic from the user
point-of-view. What Openbaton doesn't do is a smart resource utilization:
Harbor, in fact, during a NS deletion, it checks if any related VNF remains
orphan (which means without any NS using it). In that case the VNF will enter in
a state of pruning: after five minutes, if the VNF has not be re-utilized by any
other NS it will be deleted. This mechanism assure faster deployments in
environments where NSs are continuously taken up and down. \todo{I've made an
  Harbor implementation schema, I dunno if its useful to put it here}

@@

\subsubsection{Roulette Controller}
\label{chap:prjan:sec:tech:sub:SFC:sub:roulette}
Dynamic communications between VNFs would not be possible without a third
component acting as a route controller. Roulette fulfills this role, providing a
back-end where the single VNF can ask the next packet hop. Indeed, routes must 
be
submitted by another component, that we identified as Harbor (component
description available above in
sub-section~\ref{chap:prjan:sec:tech:sub:MANO:sub:harbor}). After a NS
deployment, Roulette gets instructed with a new route describing a NS. Every NS
has a proper ID (called \verb!sfid!), and thus when the classifier checks a
packet typology, it labels that packet with the specific NS ID (for a detailed
description about the SFC header see Section~\todo{Add section/chapter/paragraph
  ref!}). Finally, thanks to this label, every VNF knows the packet's chain and
it will correctly forward the it to the next VNF.

>>>>

@@

\subsubsection{Roulette Controller}
\label{chap:prjan:sec:tech:sub:SFC:sub:roulette}
Dynamic communications between VNFs would not be possible without a third
component acting as a route controller. Roulette fulfills this role, providing a
back-end where the single VNF can ask the next packet hop. Indeed, routes must 
be
submitted by another component, that we identified as Harbor (component
description available in
section~\ref{chap:archimpl:sec:secondattempt:sub:harbor}). After a NS
deployment, Roulette gets instructed with a new route describing a NS. Every NS
has a proper ID (called \verb!sfid!), and thus when the classifier checks a
packet typology, it labels that packet with the specific NS ID (for a detailed
description about the SFC header see Section~\todo{Add section/chapter/paragraph
  ref!}). Finally, thanks to this label, every VNF knows the packet's chain and
it will correctly forward the it to the next VNF.

### 2018-11-27 res/sections/15-ArchitecturalImplementation.tex
Move Harbor section from 10 to 15. Add Harbor schema

The impossibility to develop a custom VIM driver and VNFM manager lead us to
search for an alternative solution. Then, we started to work directly on the
VIM. The base approach was to create an API Server which in future an Openbaton
plugin could contact and simply deploy TOSCA definitions, interacting with a set
of RESTful APIs.

>>>>

The impossibility to develop a custom VIM driver and VNFM manager lead us to
search for an alternative solution. Then, we started to work directly on the
VIM. The base approach was to create an API Server which in future an Openbaton
plugin could contact and simply deploy TOSCA definitions, interacting with a set
of RESTful APIs. We called this simple backend \emph{Harbor}.

\subsubsection{Harbor}
\label{chap:archimpl:sec:secondattempt:sub:harbor}
Started to offer a bridge between Openbaton and Kubernetes, during the project 
it has been expanded to become a complete replacement of the original product, 
adding the possibility to manage Network Services and to update the routing 
tables contained in the Roulette Controller (the tool description can be found 
in~\ref{chap:prjan:sec:tech:sub:SFC:sub:roulette}). Harbor doesn't have a web 
interface, but as already written it has a RESTful API that allows users to 
interact with it using CRUD operations. It offers functionalities similar to 
Openbaton: possibility to save and retrieve VNF and SFC definitions (basically, 
Kubernetes YAML deployments). When an SFC is saved, a consistency check is 
performed to assure that all the VNFs have already been defined in Harbor. On 
an SFC deployment, with a mechanism similar to the Openbaton one, all the 
associated VNFs are set up too, making the whole operation of launching a SFC 
atomic from the user point-of-view. What Openbaton doesn't do is a smart 
resource utilization: Harbor, in fact, during an SFC deletion, it checks if any 
related VNF remains orphan (which means without any SFC using it). In that case 
the VNF will enter in a state of pruning: after five minutes, if the VNF has 
not be re-utilized by any other SFC it will be deleted. This mechanism assure 
faster deployments in environments where NSs are continuously taken up and 
down.

\begin{figure}[t]
 \centering
 \includegraphics[scale=0.5]{Harbor_architecture}
 \caption[Harbor architectural schema]{Harbor architectural schema}
 \label{chap:archimpl:sec:secondattempt:img:harborarchitecture}
\end{figure}
